---
title: "Faye Harwell-Module 4-Challenges (with proper HTML syntax)"
author: "Faye Harwell"
date: "September 15, 2017"
output: html_document
---
# Ulysses Challenge!!!

## First, put the quote in R

```{r}
quote<-"Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."

## Keeping the quotation marks of the quote!
quote2<-gsub("[[:punct:]]", "",quote) #keeping the quotes!

quote2
```


## Unlisting... of words in the quote

```{r}
quote3<-c(unlist(strsplit(quote2, " ")))

quote3
```

## Extract every third word from this beautiful quote

```{r}
extractedwords<-quote3[seq(from=1, to=22,by=3)]

extractedwords
```

## Remove the quote marks from R notation

```{r}
noquote(extractedwords)->finalextractedwords

finalextractedwords
```

# Primate List Challenge

## Take a bottom-up approach to this assignment (...meaning lists within lists)

### Organize the Strepsirhini!

```{r}
Lemuroidea<-list("Cheirogaleidae","Lepilemuridae","Indriidae","Lemuridae","Daubentoniidae")
names(Lemuroidea)<-c("Cheirogaleidae","Lepilemuridae","Indriidae","Lemuridae","Daubentoniidae")
Lorisoidea<-list("Lorisidae","Galagidae")
names(Lorisoidea)<-c("Lorisidae","Galagidae")
Strepsirhini<-list(Lemuroidea,Lorisoidea)
names(Strepsirhini)<-c("Lemuroidea","Lorisoidea")
```

### Now... organize the Haplorhini!

```{r}
Platyrrhini<-list("Cebidae","Atelidae","Pitheciidae")
names(Platyrrhini)<-c("Cebidae","Atelidae","Pitheciidae")
Catarrhini<-list("Cercopithecidae","Hylobatidae","Hominidae")
names(Catarrhini)<-c("Cercopithecidae","Hylobatidae","Hominidae")
Anthropoidea<-list(Platyrrhini,Catarrhini)
names(Anthropoidea)<-c("Platyrrhini","Catarrhini")
Tarsioidea<-list("Tarsiidae")
names(Tarsioidea)<-c("Tarsiidae")
Haplorhini<-list(Anthropoidea,Tarsioidea)
names(Haplorhini)<-c("Anthropoidea","Tarioidea")
```

## Now... unite them! Primates Rule!

```{r}
Primates<-list(Strepsirhini,Haplorhini)
names(Primates)<-c("Strepsirhini","Haplorhini")
Primates
```

# Challenge 3- Matrix to Data Frame

## Step 1: Make da Matrix

```{r}
matrix<- matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow=5, ncol=3, byrow=TRUE)

matrix
```

## Step 2: Coerce the Matrix to a Data Frame... It's a hard-knock life for matrices

```{r}
data.frame(matrix)->dataframe

dataframe 
```

## Step 3: Coerce the second column to be logical-valued. Isn't it just so logical? 

```{r}
as.logical(dataframe$X2)->logical

logical
```

## Step 4: Coerce the third column to be factor-valued.... Factor me into your great R plans!

```{r}
as.factor(dataframe$X3)->factor

factor
```

## Step 5: Now... let's remove the previous thing a lings...

```{r}
dataframe[,-2:-3]->clean.dataframe

clean.dataframe
```

## Step 6: Mix n' Match... Bind the two new vectors with the first column of the original dataframe

```{r}
cbind(clean.dataframe,logical,factor)->bounded

bounded

str(bounded)
str(clean.dataframe)
str(logical)
str(factor)
```
